Chatbots and messaging platforms in the classroom: an analysis from the teacher's perspective

### 2022-01-25 edubots_surveys.Rnw
Uncomment names refs #78

% Remember to substitute figures/ by nothing in the generated PDF
% \author[
%   addressref={aff1},                  
%   corref={aff1},                      
%   email={jmerelo@ugr.es}  
% ]{\inits{JJM}\fnm{Juan J.} \snm{Merelo}}
% \author[
%   addressref={aff1},
%   email={pacv@ugr.es}
% ]{\inits{PAC}\fnm{Pedro A.} \snm{Castillo}}
% \author[
%   addressref={aff2},
%   email={amorag@ugr.es}
% ]{\inits{AMM}\fnm{Antonio M.} \snm{Mora}}
% \author[
%   addressref={aff1},
%   email={fbarranco@ugr.es}
% ]{\inits{FB}\fnm{Francisco} \snm{Barranco}}
% \author[
%   addressref={aff3},
%   email={n.h.abbas@leeds.ac.uk}
% ]{\inits{NA}\fnm{Noorhan} \snm{Abbas}}
% \author[
%   addressref={aff1},
%   email={aguillen@ugr.es}
% ]{\inits{AG}\fnm{Alberto} \snm{Guillén}}
% \author[
%   addressref={aff4},
%   email={o.tsivitanidou@cyens.org.cy}
% ]{\inits{OT}\fnm{Olia} \snm{Tsivitanidou}}
% 
% \address[id=aff1]{%                           
%   \orgdiv{Department of Computer Architecture and Technology},           
%   \orgname{University of Granada},
%   \city{Granada},
%   \cny{Spain}
% }
% \address[id=aff2]{%
%   \orgdiv{Department of Signal Theory, Telematics and Communications},
%   \orgname{University of Granada},
%   \city{Granada},
%   \cny{Spain}
% }
% \address[id=aff3]{%
%   \orgdiv{School of Computing},
%   \orgname{University of Leeds},
%   \city{Leeds},
%   \cny{UK}
% }
% \address[id=aff4]{%
%   \orgname{CYENS},         
%   \city{Nicosia},
%   \cny{Cyprus} 
% }
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%                                          %%
%% Enter short notes here                   %%
%%                                          %%
%% Short notes will be after addresses      %%
%% on first page.                           %%
%%                                          %%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%\begin{artnotes}
%%\note{Sample of title note}     % note to the article
%\note[id=n1]{Equal contributor} % note, connected to author
%\end{artnotes}

>>>>

% Remember to substitute figures/ by nothing in the generated PDF
\author[
  addressref={aff1},
  corref={aff1},
  email={jmerelo@ugr.es}
]{\inits{JJM}\fnm{Juan J.} \snm{Merelo}}
\author[
  addressref={aff1},
  email={pacv@ugr.es}
]{\inits{PAC}\fnm{Pedro A.} \snm{Castillo}}
\author[
  addressref={aff2},
  email={amorag@ugr.es}
]{\inits{AMM}\fnm{Antonio M.} \snm{Mora}}
\author[
  addressref={aff1},
  email={fbarranco@ugr.es}
]{\inits{FB}\fnm{Francisco} \snm{Barranco}}
\author[
  addressref={aff3},
  email={n.h.abbas@leeds.ac.uk}
]{\inits{NA}\fnm{Noorhan} \snm{Abbas}}
\author[
  addressref={aff1},
  email={aguillen@ugr.es}
]{\inits{AG}\fnm{Alberto} \snm{Guillén}}
\author[
  addressref={aff4},
  email={o.tsivitanidou@cyens.org.cy}
]{\inits{OT}\fnm{Olia} \snm{Tsivitanidou}}

\address[id=aff1]{%
  \orgdiv{Department of Computer Architecture and Technology},
  \orgname{University of Granada},
  \city{Granada},
  \cny{Spain}
}
\address[id=aff2]{%
  \orgdiv{Department of Signal Theory, Telematics and Communications},
  \orgname{University of Granada},
  \city{Granada},
  \cny{Spain}
}
\address[id=aff3]{%
  \orgdiv{School of Computing},
  \orgname{University of Leeds},
  \city{Leeds},
  \cny{UK}
}
\address[id=aff4]{%
  \orgname{CYENS},
  \city{Nicosia},
  \cny{Cyprus}
}
